AmphibBio

### 2019-05-13 data-raw/amphibio.Rmd
Match amphibian traits to ID's

amph_ids <- by_name(amph$Species, "itis") %>%
  filter(taxonRank == "species") %>% #only want ID's to species, since that's the level of the trait data
  drop_na(acceptedNameUsageID)
```

>>>>

amph_ids <- amph %>%
  mutate(id = get_ids(Species, "itis")) %>%
  filter(!is.na(id))

# Using by_ doesn't give any additional ids
# amph_ids <- by_name(amph$Species, "itis") %>%
#   filter(taxonRank == "species") %>% #only want ID's to species, since that's the level of the trait data
#   drop_na(acceptedNameUsageID)

```
